---
title: "Rats Abrolhos"
author: "Tati Micheletti / Instituto Brasileiro para Medicina da Conserva??o"
date: "28 September 2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require("reproducible")
Require("secr")
googledrive::drive_auth(email = gargle::gargle_oauth_email(),
                        use_oob = gargle::gargle_oob_default())
```

## Abrolhos 2019
### Santa Barbara 1

```{r SB1, echo = FALSE}
captureSB1path <- preProcess(url = "https://drive.google.com/open?id=1YJEDbTS2Hs5m1LIPJNXzHYbRQMKREYoD", 
                  targetFile = "capture1.txt", 
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

detectorSB1path <- preProcess(url = "https://drive.google.com/open?id=1Dtzab2-EIWVPZl5bPcG97xEfQzA0kfN-", 
                  targetFile = "detector1.txt",
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

SB1 <- secr::read.capthist(captfile =  captureSB1path$targetFilePath, 
                           trapfile = detectorSB1path$targetFilePath)

summary(SB1)
g0.1 <- secr.fit(SB1, model = list(g0 ~ 1, sigma ~ 1), CL = TRUE,
               verify = FALSE, buffer = 200)

densitySB1 <- derived(g0.1)
```

Home range results (sigma estimate, lcl = lowe95%CI; ucl = upper95%CI):
```{r, echo = FALSE}
knitr::kable(summary(g0.1)$predicted)
```

Density results (D estimate, lcl = lowe95%CI; ucl = upper95%CI):
```{r, echo = FALSE}
knitr::kable(densitySB1)
```

### Santa Barbara 2

```{r SB2, echo = FALSE}
captureSB2path <- preProcess(url = "https://drive.google.com/open?id=1CXe-u9x41OtBCgLMhXP7o1OtpxZ0c0nr", 
                  targetFile = "capture2.txt", 
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

detectorSB2path <- preProcess(url = "https://drive.google.com/open?id=1M2mdWYVITY8pz4j5AWppQoX-dm5it04I", 
                  targetFile = "detector2.txt",
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

SB2 <- secr::read.capthist(captfile =  captureSB2path$targetFilePath, 
                           trapfile = detectorSB2path$targetFilePath)

summary(SB2)
g0.2 <- secr.fit(SB2, model = list(g0 ~ 1, sigma ~ 1), CL = TRUE,
               verify = FALSE, buffer = 200)

densitySB2 <- derived(g0.2)
```

Home range results (sigma estimate, lcl = lowe95%CI; ucl = upper95%CI):
```{r, echo = FALSE}
knitr::kable(summary(g0.2)$predicted)
```

Density results (D estimate, lcl = lowe95%CI; ucl = upper95%CI):
```{r, echo = FALSE}
knitr::kable(densitySB2)
```

## RESULTS

For Santa Barbara 1, we have **65** rats/ha (CI95%: 12-358), 
with home range of **16.75m** (CI95%: 3.66-76.82).  

For Santa Barbara 2, we have **2.17** rats/ha (CI95%: 0.34-14), 
with home range of **40m** (CI95%: 11.12-143.93).  

Obs.: In my opinion, the deviation is really too big. We need to collect more data (ie. trapping for longer time and probably with a bigger grid...) ~TM


### Siriba 1

```{r Si1, echo = FALSE}
captureSi1path <- preProcess(url = "https://drive.google.com/open?id=18vh4aGPZ_2u280vMOdro_O1DMOT2cyxW", 
                  targetFile = "capture3.txt", 
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

detectorSi1path <- preProcess(url = "https://drive.google.com/open?id=1JywW6MS8uoyVwKUYQ1A_MBtJEL5h43lg", 
                  targetFile = "detector3.txt",
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

Si1 <- secr::read.capthist(captfile =  captureSi1path$targetFilePath, 
                           trapfile = detectorSi1path$targetFilePath)

summary(Si1)
g0.1 <- secr.fit(Si1, model = list(g0 ~ 1, sigma ~ 1), CL = TRUE,
               verify = FALSE, buffer = 200)

densitySi1 <- derived(g0.1)
```

Home range results (sigma estimate, lcl = lowe95%CI; ucl = upper95%CI):
```{r, echo = FALSE}
knitr::kable(summary(g0.1)$predicted)
```

Density results (D estimate, lcl = lowe95%CI; ucl = upper95%CI):
```{r, echo = FALSE}
knitr::kable(densitySi1)
```

## RESULTS

For Siriba 1, we have **69** rats/ha (CI95%: 52-93), 
with home range of **7.76m** (CI95%: 6.64-9.07).  

## Abrolhos 2020
### Santa Barbara 1

```{r SB1.4, echo = FALSE}
library(reproducible)
library(secr)
captureSB4path <- preProcess(url = "https://drive.google.com/open?id=1EJlxxQYyj4CwZcDrdEoA8J5kerihyEQe", 
                  targetFile = "capture4.txt", 
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

detectorSB4path <- preProcess(url = "https://drive.google.com/open?id=1w3eijp6dhYGDIINXoZPwNZeMMW9ykVkQ", 
                  targetFile = "detector4.txt",
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

SB1.4 <- secr::read.capthist(captfile =  captureSB4path$targetFilePath, 
                           trapfile = detectorSB4path$targetFilePath)

summary(SB1.4)
g0.4 <- secr.fit(SB1.4, model = list(g0 ~ 1, sigma ~ 1), CL = TRUE,
               verify = FALSE, buffer = 200)

# densitySB1.4 <- secr::derived(g0.4)
```

<!-- Home range results (sigma estimate, lcl = lowe95%CI; ucl = upper95%CI): -->
<!-- ```{r, echo = FALSE} -->
<!-- knitr::kable(summary(g0.4)$predicted) -->
<!-- ``` -->

<!-- Density results (D estimate, lcl = lowe95%CI; ucl = upper95%CI): -->
<!-- ```{r, echo = FALSE} -->
<!-- knitr::kable(densitySB1.4) -->
<!-- ``` -->

## RESULTS

Data sparse, model fitting failed (i.e. potentially because not all individuals were marked)
<!-- For Santa Barbara 1 (2020), we have **69** rats/ha (CI95%: 52-93),  -->
<!-- with home range of **7.76m** (CI95%: 6.64-9.07).   -->

### Santa Barbara 2

```{r SB1.5, echo = FALSE}
library(reproducible)
library(secr)
captureSB5path <- preProcess(url = "https://drive.google.com/open?id=1DB7G3x90cQtdPV_XDRuTG3IXcvBDXbu2", 
                  targetFile = "capture5.txt", 
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

detectorSB5path <- preProcess(url = "https://drive.google.com/open?id=1mmsxpM3ET_Q4hqbCGz-q3EcncZFVPiNS", 
                  targetFile = "detector5.txt",
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

SB1.5 <- secr::read.capthist(captfile =  captureSB5path$targetFilePath, 
                           trapfile = detectorSB5path$targetFilePath)

summary(SB1.5)
g0.5 <- secr.fit(SB1.5, model = list(g0 ~ 1, sigma ~ 1), CL = TRUE,
               verify = FALSE, buffer = 200)

densitySB1.5 <- secr::derived(g0.5)
```

Home range results (sigma estimate, lcl = lowe95%CI; ucl = upper95%CI):
```{r, echo = FALSE}
knitr::kable(summary(g0.5)$predicted)
```

Density results (D estimate, lcl = lowe95%CI; ucl = upper95%CI):
```{r, echo = FALSE}
knitr::kable(densitySB1.5)
```

## RESULTS

Data sparse, model fitting failed (i.e. potentially because not all individuals were marked)
For Santa Barbara 2 (2020), we have **14** rats/ha (CI95%: 10-23),
with home range of **19m** (CI95%: 16-24).

### Redonda 1

```{r R1, echo = FALSE}
library(reproducible)
library(secr)
captureR1path <- preProcess(url = "https://drive.google.com/open?id=1xblSTYnZ9B4pSEXJwHYnU7UtxF6Rius9", 
                  targetFile = "capture6.txt", 
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

detectorR1path <- preProcess(url = "https://drive.google.com/open?id=1Pmb2y293I0TnnxeWXuq73ChgpvdLN7AZ", 
                  targetFile = "detector6.txt",
                  destinationPath = reproducible::checkPath(file.path(getwd(), "data"), 
                                                            create = TRUE), overwrite = TRUE)

R1 <- secr::read.capthist(captfile =  captureR1path$targetFilePath, 
                           trapfile = detectorR1path$targetFilePath)

summary(R1)
g0.6 <- secr.fit(R1, model = list(g0 ~ 1, sigma ~ 1), CL = TRUE,
               verify = FALSE, buffer = 200)

densityR1 <- secr::derived(g0.6)
```

Home range results (sigma estimate, lcl = lowe95%CI; ucl = upper95%CI):
```{r, echo = FALSE}
knitr::kable(summary(g0.6)$predicted)
```

Density results (D estimate, lcl = lowe95%CI; ucl = upper95%CI):
```{r, echo = FALSE}
knitr::kable(densityR1)
```

## RESULTS

For Redonda 1 (2020), we have *27* rats/ha (CI95%: 18-38),
with home range of *16m* (CI95%: 13-19).
